---
title: "Final Project for Developing Data Products"
author: "Mary0523"
date: "October 14, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
- This project contains two parts. This is the second part:  
use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

- Requirement: 
1. 5 slides to pitch our idea done in Slidify or Rstudio Presenter
2. Your presentation pushed to github or Rpubs
3. A link to your github or Rpubs presentation pasted into the provided text box

## App and R code

###This application is used to calculate due date for baby.
Link for the application: https://mary0523.shinyapps.io/myapp/
- The application requires entering: 
   1. the pregnancy women's first day of last menstrual period
   2. the pregnancy women's average menstrual period cycle duration (default is 28 days)

- Click on "Get my due date"

- On the up right side of the website you will get the estimated due date  

The formula used by this application is adaped from [Naegele's rule][1]

[1]:https://ipfs.io/ipfs/QmXoypizjW3WknFiJnKLwHCnL72vedxjQkDDP1mXWo6uco/wiki/Naegele's_rule.html

## Formula used for due date calculation
```{r, echo = TRUE}
#First day of last menstrual period
date1<-as.numeric(as.Date("2018-10-14",origin = "1970-01-01"))
#Average cycle duration
duration<-28
#Estimated due date
as.Date(date1+(273-21+duration),origin = "1970-01-01")
```

## Thank you for watching!!
###Link to R code for the application and this presentation is on github 


